R Notebook

### 2017-08-01 doc/RMD/wmn-differentiation.Rmd
Add test for NE WA, and MI

```{r AMOVA-Region, cache = TRUE}
ssc_amova_region <- poppr.amova(dat11cc, ~SourceType/Region, dist = bd, quiet = TRUE)
ssc_amova_region_test <- randtest(ssc_amova_region, nrepet = 999)
plot(ssc_amova_region_test)
(ssc_amova_table <- make_amova_table(ssc_amova_region, ssc_amova_region_test))
```

@@

```{r AMOVA_table, comment = NA}
make_amova_printable(ssc_amova_table, ssc_amova_nm_table) %>%  
  as_tibble() %>%
  add_column(Hierarchy = c("Between Source", "Between Region within Source", "Within Region"), .before = 1) %>%
  readr::write_csv(path = file.path("results", "tables", "AMOVA-region.csv"), col_names = TRUE) %>%
  rename(ps = `Phi statistic`) %>%
  mutate(ps = gsub("0\\.00(\\d{1})(\\d{2})", "\\1.\\2e^-3^", ps)) %>%
  mutate(ps = case_when(Hierarchy == "Between Source" ~ ps, TRUE ~ paste0("**", ps, "**"))) %>%
  rename(`$\\Phi statistic$` = ps) %>%
  rename(`% variation` = `Percent variation`) %>%
  rename(S.S. = `Sum of Squares`) %>%
  select(-P) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>% 
  huxtable::set_col_width(c(1.1, 0.6, 0.9, 0.9, 1.4)) %>% 
  huxtable::set_align(huxtable::everywhere, 2:5, "center") %>% 
  huxtable::print_md(max_width = 100)
```

When we remove the Mexican isolates (which only contained white mold nurseries
and shared no genotypes), we see that indeed, the degree of differentiation
went down.

>>>>

```{r AMOVA-Region, cache = TRUE}
ssc_amova_region <- poppr.amova(dat11cc, ~SourceType/Region, dist = bd, quiet = TRUE)
ssc_amova_region_test <- randtest(ssc_amova_region, nrepet = 9999)
plot(ssc_amova_region_test)
(ssc_amova_table <- make_amova_table(ssc_amova_region, ssc_amova_region_test))
```

@@

When we remove the Mexican isolates (which only contained white mold nurseries
and shared no genotypes), we see that indeed, the degree of differentiation
went down.  Of course, if we look at the distribution of isolates between white
mold nurseries and regions, we can see things are a bit lopsided:

```{r wmntable}
table(strata(dat11cc, ~SourceType/Region, combine = FALSE))
```

The only regions that have at least ten samples in both white mold nurseries and
production regions are NE, WA, and MI. We can see what happens when we subsample
to these

```{r AMOVA-newami, cache = TRUE}
datnewami <- setPop(dat11cc, ~Region) %>% popsub(sublist = c("NE", "WA", "MI"))
bdnewami     <- bruvo.dist(datnewami, replen = other(datnewami)$REPLEN)
ssc_amova_newami <- poppr.amova(datnewami, ~SourceType/Region, dist = bdnewami, quiet = TRUE)
ssc_amova_newami_test <- randtest(ssc_amova_newami, nrepet = 9999)
plot(ssc_amova_newami_test)
(ssc_amova_newami_table <- make_amova_table(ssc_amova_newami, ssc_amova_newami_test))
```

```{r AMOVA_table, comment = NA}
make_amova_printable(ssc_amova_table, ssc_amova_newami_table) %>%  
  as_tibble() %>%
  add_column(Hierarchy = c("Between Source", "Between Region within Source", "Within Region"), .before = 1) %>%
  readr::write_csv(path = file.path("results", "tables", "AMOVA-region.csv"), col_names = TRUE) %>%
  rename(ps = `Phi statistic`) %>%
  mutate(ps = gsub("0\\.00(\\d{1})(\\d{2})", "\\1.\\2e^-3^", ps)) %>%
  mutate(ps = case_when(Hierarchy == "Between Source" ~ ps, TRUE ~ paste0("**", ps, "**"))) %>%
  rename(`$\\Phi statistic$` = ps) %>%
  rename(`% variation` = `Percent variation`) %>%
  rename(S.S. = `Sum of Squares`) %>%
  select(-P) %>%
  huxtable::as_huxtable(add_colnames = TRUE) %>% 
  huxtable::set_col_width(c(1.1, 0.6, 0.9, 0.9, 1.4)) %>% 
  huxtable::set_align(huxtable::everywhere, 2:5, "center") %>% 
  huxtable::print_md(max_width = 100)
```
